Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
rev

\begin{frame}{ML-Like: Path-Dependent Types}
\begin{itemize}
\item Scala's abstract types  $\approx$ ML's abstract types of signatures; limitations:
\begin{itemize}
\item recursive references
\item bounded quantifications
\end{itemize}
\item translucent sum can be given a more precise type by referring to the name of its type member with a path selection; essential for
\begin{itemize}
\item breaking the dependencies between (sub)fields
\item propagation of typing information
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Tribe Calculus: Virtual Classes}
\begin{itemize}
\item {\it familes} of classes inherited together
\item classes are lexically nested inside other classes: when a class
  is inherited, its nested inner classes are inherited along with
  their methods and fields
\item two form of inheritance: subclassing and further binding
\item {\it family polymorphism}: code written for one family
  also works for extensions of that family
\item in Tribe:\begin{itemize}
\item path types can depend simultaneously on both classes and objects
\item paths can use an {\tt out} field to move from an object to the
  object which surrounds it; enables ubiquitous access to an object's
  family without the need to drag around family arguments
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Tribe: Discussion}
\begin{itemize}
\item no virtual classes in Scala; its virtual types can emulate some (but not all) of the benefits
\item because of {\tt out} field, Tribe has limited cross-family inheritance
\item soundness? substitution lemma seems wrong when {\tt null} is
  substituted for a variable in an expression whose type contains
  that variable
\item aims to have decidable type-checking, but still not proved so
\end{itemize}
\end{frame}

>>>>

\begin{frame}{ML-Like: Path-Dependent Types}
\begin{itemize}
\item Scala's abstract types  $\approx$ ML's abstract types of signatures; limitations:
\begin{itemize}
\item recursive references
\item bounded quantifications
\end{itemize}
\item translucent sum can be given a more precise type by referring to the name of its type member with a path selection; essential for %example?
\begin{itemize}
\item breaking the dependencies between (sub)fields
\item propagating typing information
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Tribe Calculus: Virtual Classes}
\begin{itemize}
\item {\it families} of classes inherited together
\item classes are lexically nested inside other classes: when a class
  is inherited, its nested inner classes are inherited along with
  their methods and fields
\item two form of inheritance: subclassing and further binding
\item {\it family polymorphism}: code written for one family
  also works for extensions of that family
\item in Tribe:\begin{itemize}
\item path types can depend simultaneously on both classes and objects
\item paths can use an {\tt out} field to move from an object to the
  object which surrounds it; enables ubiquitous access to an object's
  family without the need to drag around family arguments
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Tribe: Discussion}
\begin{itemize}
\item no virtual classes in Scala; its virtual types can emulate some (but not all) of the benefits
\item because of {\tt out} field, Tribe has limited cross-family inheritance %example?
\item soundness? substitution lemma seems wrong when {\tt null} is
  substituted for a variable in an expression whose type contains
  that variable %details?
\item aims to have decidable type-checking, but still not proved so
\end{itemize}
\end{frame}
